DATA 621 - Business Analytics and Data Mining

### 2020-11-02 HW4/HW4_Draft.Rmd
Add a cache so that those with slower computers don't have to recalc the frequency model every time.

```{r model1RunFreq}
trC <- trainControl(method = 'none',            # Using StepAIC
                    classProbs = TRUE,          # Classification
                    summaryFunction = prSummary # Precision/Recall)
)
set.seed(487)
m1FreqFit <- train(x = trnXFD, y = trnFreq, preProcess = c('nzv', 'knnImpute'),
                   trControl = trC, method = 'glmStepAIC',
                   family = binomial(link = 'logit'), direction = 'both',
                   trace = 1)
kable(summary(m1FreqFit)$coefficients, digits = 3L,
      caption = "Model 1 Frequency Regression Output")
```

>>>>

```{r model1RunFreq, cache = 2}
trC <- trainControl(method = 'none',            # Using StepAIC
                    classProbs = TRUE,          # Classification
                    summaryFunction = prSummary # Precision/Recall)
)
set.seed(487)
m1FreqFit <- train(x = trnXFD, y = trnFreq, preProcess = c('nzv', 'knnImpute'),
                   trControl = trC, method = 'glmStepAIC',
                   family = binomial(link = 'logit'), direction = 'both',
                   trace = 1)
kable(summary(m1FreqFit)$coefficients, digits = 3L,
      caption = "Model 1 Frequency Regression Output")
```
